Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them

### 2020-12-03 Manuscript/EPAWTFT.tex
comment on Surjan section

In a later study by the same group, they used analytic continuation techniques 
to resum a divergent MP series such as a stretched water molecule.\cite{Mihalka_2017a}
Any MP series truncated at a given order $n$ can be used to define the scaled function
\begin{equation}
   E_{\text{MP}n}(\lambda) = \sum_{k=0}^{n} \lambda^{k} E^{(k)}.
\end{equation}
Reliable estimates of the energy can be obtained for values of $\lambda$ where the MP series is rapidly
convergent (\ie, for $\abs{\lambda} < \rc$), as shown in Fig.~\ref{fig:rmp_anal_cont} for the RMP10 series 
of the symmetric Hubbard dimer with $U/t = 4.5$.
These values can then be analytically continued using a polynomial- or Pad\'e-based fit to obtain an 
estimate of the exact energy at $\lambda = 1$.
However, choosing the functional form for the best fit remains a difficult and subtle challenge.

This technique was first generalised by using complex scaling parameters and constructing an analytic
continuation by solving the Laplace equations.\cite{Surjan_2018}
It was then further improved by introducing Cauchy's integral formula\cite{Mihalka_2019}
\begin{equation}
	\label{eq:Cauchy}
    \frac{1}{2\pi \i} \oint_{\mathcal{C}} \frac{E(\lambda)}{\lambda - \lambda_1} = E(\lambda_1),
\end{equation}
which states that the value of the energy can be computed at $\lambda_1$ inside the complex 
contour $\mathcal{C}$ using only the values along the same contour.
Starting from a set of points in a ``trusted'' region where the MP series is convergent, their approach 
self-consistently refines estimates of the $E(\lambda)$ values on a contour around the physical point 
$\lambda = 1$.
The shape of this contour is arbitrary, but there must be no branch points or other singularities inside
the contour.
Once the contour values of $E(\lambda)$ are converged, Cauchy's integral formula Eq.~\eqref{eq:Cauchy} can 
be invoked to compute the value at $E(\lambda=1)$ and obtain a final estimate of the exact energy.
The authors illustrate this protocol for the dissociation curve of \ce{LiH} and the stretched water 
molecule to obtain encouragingly accurate results.\cite{Mihalka_2019}

>>>>

In a later study by the same group, they used analytic continuation techniques 
to resum a divergent MP series such as a stretched water molecule.\cite{Mihalka_2017a}
Any MP series truncated at a given order $n$ can be used to define the scaled function
\begin{equation}
   E_{\text{MP}n}(\lambda) = \sum_{k=0}^{n} \lambda^{k} \titou{E_\text{MP}^{(k)}}.
\end{equation}
Reliable estimates of the energy can be obtained for values of $\lambda$ where the MP series is rapidly
convergent (\ie, for $\abs{\lambda} < \rc$), as shown in Fig.~\ref{fig:rmp_anal_cont} for the RMP10 series 
of the symmetric Hubbard dimer with $U/t = 4.5$.
These values can then be analytically continued using a polynomial- or Pad\'e-based fit to obtain an 
estimate of the exact energy at $\lambda = 1$.
However, choosing the functional form for the best fit remains a difficult and subtle challenge.

This technique was first generalised by using complex scaling parameters and constructing an analytic
continuation by solving the Laplace equations.\cite{Surjan_2018}
It was then further improved by introducing Cauchy's integral formula\cite{Mihalka_2019}
\begin{equation}
	\label{eq:Cauchy}
    \frac{1}{2\pi \i} \oint_{\mathcal{C}} \frac{E(\lambda)}{\lambda - \lambda_1} = E(\lambda_1),
\end{equation}
which states that the value of the energy can be computed at $\lambda_1$ inside the complex 
contour $\mathcal{C}$ using only the values along the same contour.
Starting from a set of points in a ``trusted'' region where the MP series is convergent, their approach 
self-consistently refines estimates of the $E(\lambda)$ values on a contour \titou{around} the physical point 
$\lambda = 1$.
\titou{T2: actually this is not true as the point $\lambda = 1$ is chosen to be on the contour.}
The shape of this contour is arbitrary, but there must be no branch points or other singularities inside
the contour.
Once the contour values of $E(\lambda)$ are converged, Cauchy's integral formula Eq.~\eqref{eq:Cauchy} can 
be invoked to compute the value at $E(\lambda=1)$ and obtain a final estimate of the exact energy.
The authors illustrate this protocol for the dissociation curve of \ce{LiH} and the stretched water 
molecule to obtain encouragingly accurate results.\cite{Mihalka_2019}
